\documentclass[mscthesis]{usiinfthesis}
% \documentclass[12pt]{article}
\usepackage{subfiles}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage{biblatex}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{float}
\usepackage{subcaption}
\usepackage{todonotes}
\usepackage{float}
\usepackage{alphalph,etoolbox}
\let\circledS\undefined 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{multirow, multicol, makecell, booktabs}
\usepackage{bm}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcommand{\cs}[1]{\renewcommand{\tabcolsep}{#1pt}}
\usepackage{lipsum}
\usepackage{listings}

\usepackage{alphalph}
\renewcommand*{\thesubfigure}{%
\alphalph{\value{subfigure}}%
}%
% \renewcommand\thesubfigure{\arabic{subfigure}}

% \renewcommand{\thesection}{\alphalph{\value{section}}}
% \renewcommand{\thesubsubsection}{\alphalph{\value{section}}}

% \renewcommand*{\thesection}{(\value{subfigure})}

\graphicspath{{img/}{../img/}}

\title{Traversability Estimator for a Legged Robot} %compulsory
\specialization{Artificial Intelligence}%optional
% \subtitle{Subtitle: bho} %optional 
\author{Francesco Saverio Zuppichini} %compulsory
\begin{committee}
\advisor{Prof.}{Student's}{Alessandro Giusti} %compulsory
\coadvisor{Prof.}{Student's}{Omar Chavez-Garcia}{}
\end{committee}
\Day{26} %compulsory
\Month{June} %compulsory
\Year{2019} %compulsory, put only the year
\place{Lugano} %compulsory
%\addbibresource{bibliography.bib}

\begin{document}

\maketitle %generates the titlepage, this is FIXED

\frontmatter %generates the frontmatter, this is FIXED

\subfile{./tex/abstract.tex}
\begin{acknowledgements}
    I would like to thank my family for always supporting me. All my friends from USI and Verona. 
    Especially Dario, one of the most positive person that I know, that helped during my Thesis always with a big smile. Thanks to Alessia and her big patience.  To Nicola, Federico, Paolo and Alessandro to always make my weekends here in Italy specials. Thank you guys for making me laughing since high school. 

    To my advisor and co-advisor, Professor Giusti and Omar Chavez-Garcia to give me this amazing opportunity to work on a project I loved. Thank you Omar to helped me out through all these months, I could have been there without you. 
    
    Finally I would like to thank all the professors who taught me unforgettable subjects.
    \end{acknowledgements}
\tableofcontents 
% \listoffigures
% \listoftables

\mainmatter

% \input{./tex/abstract.tex}
% \input{./tex/introduction.tex}
% \input{./tex/chapter1.tex}
% \input{./tex/chapter3.tex}
% \input{./tex/chapter4.tex}
% \input{./tex/chapter5.tex}

% \clearpage
\subfile{./tex/introduction.tex}
%\clearpage
\subfile{./tex/chapter1.tex}
%\clearpage

\subfile{./tex/chapter2.tex}
% TODO

\subfile{./tex/chapter3.tex}
%\clearpage
\subfile{./tex/chapter4.tex}
%\clearpage
\subfile{./tex/chapter5.tex}
%\clearpage
\subfile{./tex/conclusion.tex}
%\clearpage

\backmatter

%\printbibliography
\bibliographystyle{abbrv}
\bibliography{bibliography}

\end{document}
